Learning a functional distance between organizations with unsupervised embeddings of scientific mobility

### 2020-09-14 paper/current/main.tex
change a little bit

>>>>

\subsection*{Data -US Airport Itinerary}
We use US airport itinerary data from the Bureau of Transportation statistics provided by the United States Department of Transportation. Origin and Destination Survey (DB1B) is a 10\% sample of domestic airline tickets, including origin, destination, and other itinerary details. Trajectories are represented as the list of airport code and cover itinerary between 1993 to 2020. There are 30,776,0841 trajectories in total and the unique number of airports is 838.
